Differences in security between the last and the current governments in Mexico 
========================================================

Last Presidential term (2006-2012) in Mexico was characterized for the violence generated by the war against drug cartels. The current president claims belongs to a different party and he claimed that his security strategy would be more effective. 

In this work, I will try to analize different security indicators for different Presidential terms: 2000-2006, 2006-2012 and 2012-present to see if there are clear differences in security betweeen goverments. 

The website <a href="http://crimenmexico.diegovalle.net/en/">http://crimenmexico.diegovalle.net/en/</a> cointains plenty of illustrative plots that give some ideas of the variables. The data was extracted from the webpage of <a href = "http://www.secretariadoejecutivo.gob.mx/es/SecretariadoEjecutivo/Incidencia_Delictiva">Secretariado Ejecutivo del Sistema Nacional de Seguridad Pública </a>.

The data some irregularities, such as events not recorded for some periods of time, but I will try to do the best I can.

```{r}
## I will delete this later.
summary(cars)
```

```{r fig.width=7, fig.height=6}
suppressMessages(library(ggplot2))
qplot(speed, dist, data = cars, geom = "point", main = "Just a sample plot")
```

